Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:14	20:25:22	(Fri14.Aug)

\begin{figure}[tbhp]%\centering%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

@@

@@

3rd order Maclaurin / Tayler approximation
\begin{align}
\phi_\text{-3dB bounds} \approx -0.002894\beta^3 + 0.02451\beta^2 + -0.01308\beta + 0.2980
\end{align}

There is an upper bound to how much a window should be steered. Since each window's response is constrained to a unit gain in the look direction, each steered window's response is gained as shown in \Fig{window_steering}. moreUnder the constraint of a unit gain in the look direction, the effect of 
When steering the windows it is desirable to limit the amount of steering

Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.

% \begin{align}
% \z = \w\H\a 
% \end{align}

% 
% Narrow ones:
% - Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
% 
% 
% Beamforming:
% - Maximize resolution
% - Minimize noise/error, both coherent and incoherent
% - Minimize signal cancellation
% 
% Gauss: Miminized time-bandwidth product
%   - 
%   
% Rectangular
%   - 
% Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
% Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.
% 
% Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.

>>>>

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/calc_kaiser_3dB.pdf}%
\caption{Each Kaiser window is steered in the interval $\phi=[0, \phi_{\text{-3dB}}(\beta)]$. The angle $\phi_{\text{-3dB}}(\beta)$ is the amount of steering needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.}\label{windows_steering}
\end{figure}

@@

The steering is subject to an upper steering bound specified, which will be discussed next.

@@

There is an upper bound to the amount of steering we should apply to a window. Since each window's response is constrained to a unit gain in the look direction, each steered window's response is gained as shown in \Fig{windows_steering}. This increases the white noise gain and deteriorates the signal to noise ratio. To limit this we placing an upper bound to the steering, taking into account that a wide window can be allowed more steering than a narrow one.

We call the upper bound for steering $\phi_{\text{-3dB}}(\beta)$, and define it as the steering angle needed for the steered response to have a -3dB crossing that is exactly half that of the unsteered window. We numerically searched for the steering angle $\phi$ that fulfilled this criterion for a wide range of $\beta$-values. An explicit expression for was finally obtained with a third degree polynomial fit:
%
\begin{align}
\phi_\text{-3dB}(\beta) \approx -0.002894\beta^3 + 0.02451\beta^2 + -0.01308\beta + 0.2980
\end{align}
%
Any steering will be specified relative to this upper bound. With each window steered this way we expect the resolution gain to remain predictable and independent of $\beta$, and we also effectively constrain the white noise gain of the beamformer.

% Narrow ones:
% - Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
% 
% 
% Beamforming:
% - Maximize resolution
% - Minimize noise/error, both coherent and incoherent
% - Minimize signal cancellation
% 
% Gauss: Miminized time-bandwidth product
%   - 
%   
% Rectangular
%   - 
% Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
% Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.
% 
% Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.
